\documentclass[11pt]{article}

% set the margin. This is wider than usual to allow for more horizontal workspace
\usepackage[margin=0.5in]{geometry}

\begin{document}

\vspace*{0.5in}

\begin{center}
\Huge{{\bf IE332 Assignment \# X}}
\end{center}

\vspace{0.3in}

\noindent We certify that the submitted work does not violate any academic misconduct rules, and that it is solely our own work. By listing our names we acknowledge that any misconduct will result in appropriate consequences.  Moreover, we have {\bf read and understood the assignment and project instructions} and agree that the below individual evaluation is correct.

\vspace{0.2in}

\noindent {\em ``As a Boilermaker pursuing academic excellence, we pledge to be honest and true in all that we do. Accountable together - we are Purdue.''}

\vspace{0.3in}

\noindent FULL name of each team member (Lastname, Firstname) as indicated in Brightspace (no PUIDs!). Complete the table as explained in the project description and highlighted below the table:

\vspace{0.1in}

% replace small with footnotesize if the horizontal space is required
{\small
\begin{tabular}{l | c c | c c || r r }
Student & Q1 & Q2 & Overall & DIFF & Officer & S/I \\
\hline
A &  &  &  &  & & \\
B &  &  &  &  & & \\
C &  &  &  &  & & \\
D &  &  &  &  & & \\
E &  &  &  &  & & \\
F &  &  &  &  & & \\
G &  &  &  &  & & \\
\hline 
St Dev &  &  &  & & - & - \\
\hline
\end{tabular}}

\vspace{0.2in}

\noindent where Overall is the sum of the total effort of each student. DIFF is the difference from equal contribution, and for each member is calculated as their overall score - 100*(\# of questions) / (\# group members), rounded to the nearest whole number. The last row is the rounded standard deviation of the respective column (except the last two columns which are not numeric). Indicate as well the ``Officer'' roles as outlined on the project description, and whether the person is performing Satisfactorily (S), or Inadequately (I).

\vspace{0.2in}

% automatically add the date the file was compiled into pdf
\noindent Date: \today

% ignore the cover page as a page # by resetting the page counter manually
\setcounter{page}{1}


\end{document}